Sample-efficient Reinforcement Learning \\ with Implicitly Quantized Representations

### 2024-02-01 paper/main.tex
udpated
Update to abstract

\begin{abstract}
  In reinforcement learning (RL) for continuous control, we propose an
  efficient representation learning method using only a latent-state
  consistency loss. Our approach employs an encoder and a transition
  model to map observations to latent states and predict future
  states, respectively. We achieve high performance and prevent
  representation collapse by normalizing, quantizing, and bounding the
  latent representation. Our method is straightforward, compatible
  with any model-free RL algorithm, and demonstrates state-of-the-art
  performance in continuous control benchmarks from DeepMind Control
  Suite.
\end{abstract}

>>>>

\begin{abstract}
  In reinforcement learning (RL) for continuous control, we propose an
  efficient representation learning method using only a latent-state
  consistency loss. Our approach employs an encoder and a transition
  model to map observations to latent states and predict future
  states, respectively. We achieve high performance and prevent
  representation collapse by normalizing the quantized latent
  representation such that rank in the presentation is empirically
  preserved. Our method is straightforward, compatible with any
  model-free RL algorithm, and demonstrates state-of-the-art
  performance in continuous control benchmarks from DeepMind Control
  Suite.
\end{abstract}
